Evaluating FAIR Digital Object and Linked Data as distributed object systems

### 2023-06-16 latex/main.tex
language tweak. linenos for review

\documentclass[fleqn,10pt,NOlineno]{wlpeerjlua}

@@

EOSC proposes FAIR Digital Objects as a way to improve interoperability, for instance invoked by scientific workflows, carried by metadata frameworks and semantic artefacts. Therefore we here find it important to analyse how  FDO and Linked Data can help satisfy the EOSC requirements.

>>>>

\documentclass[fleqn,10pt,lineno]{wlpeerjlua}

@@

As covered in our introduction, EOSC proposes FAIR Digital Objects as a way to improve interoperability, for instance invoked by scientific workflows, carried by metadata frameworks and semantic artefacts. Therefore we here find it important to summarize how FDO and Linked Data can help satisfy the EOSC requirements.
